A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games

### 2014-08-18 paper.tex
more

\begin{document}
%\onecolumn
\title{A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games}

@@

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\item $A^T$: \quad transpose of a matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of  a vector $v$;
\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
\item $i_C$: \quad indicator function of a convex set $C$;
\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
\end{itemize}

>>>>

\begin{document}
\onecolumn
\title{A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games}

@@

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathcal{P}(S)$: \quad set of all the subsets of $S$;
\item $\mathcal{P}_k(S)$: \quad set of all the subsets of $S$ which have exactly $k$ elements;
\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$;
\item $A^T$: \quad transpose of a matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of  a vector $v$;
\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
\item $i_C$: \quad indicator function of a convex set $C$;
\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
\end{itemize}

\subsection{Generating the Texas Hold'em Poker game tree}
Let $a := (a_1, a_2, a_3, a_4) \in 
\mathbb{R}\times\mathbb{R}\times\mathbb{R}^2\times\mathbb{R}^2$ hold the accounting info, where:
\begin{itemize}
\item $a_1\in\mathbb{R}$ is the running bet size,
\item $a_2\in\mathbb{R}$ is the running total amount in the pot,
\item $a_3\in\mathbb{R}^2$ is a vector showing what each player has put into the pot sofar, and
\item $a_4\in\mathbb{R}^2$ is a vector showing running capital of each player.
\end{itemize}
Let $ok(a, L)$ be a flag which is true iff the bet size $a_1$ has not exceeded the limit $L$ and each player's running credit is nonnegative.
For any round $t\in\mathbb{N}$, let $p(t)$ be the player to begin and $\Sigma(t)$ be the set of all signals that can be emitted by the chance player.
\definition{
A signal is simply any part of the information needed at shutdown to score the player's hands.
}
\remark{
An emitted signal can be fully observable (for example, community cards), or only partially observable (for example when private / hole / pocket cards are delt, players can only see their own hole cards given to them; they can't see another player's hole cards).
}

\begin{equation}
  \gamma(t, T, a, L) = \begin{cases} 
    \mathcal{P}_1(\Sigma(t)), &\mbox{if } (t < T) \land ok(a, L) \land (p(t) = 0);\\
            {\{\textbf{F}_{p(t)}\} \cup \textbf{C}_{p(t)}\gamma(t + 1, T, a, L) \cup \textbf{K}_{p(t)}\lambda(t, T, g(a, \textbf{K}_{p(t)}), L)},&\mbox{if } (t < T) \land ok(a, L) \land (p(t) > 0);\\
            \emptyset, &\mbox{if } t \ge T \lor \neg ok(a, L) .\end{cases}
\end{equation}
where the auxiliary function $\lambda$ is defined by:
\begin{equation}
  \left.
  \begin{aligned}
    \lambda(t, T, a, L) := \cup_{n=0}^\infty\alpha_1^{(n)}(t, T, a, L) \cup \cup_{n=0}^\infty\alpha_2^{(n)}(t, T, a, L)\\
    \alpha_1^{(n)}(t, T, a, L) := (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\mathcal{P}_1(\{\textbf{F}_{p(t)'}, \textbf{K}_{p(t)'}\})\gamma(t + 1, T, g(a, (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\mathcal{P}_1(\{\textbf{F}_{p(t)'}, \textbf{K}_{p(t)'}\})), L)\\
    \alpha_2^{(n)}(t, T, a, L) := (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\textbf{R}_{p(t)'}\mathcal{P}_1(\{\textbf{F}_{p(t)}, \textbf{K}_{p(t)}\})\gamma(t + 1, T, g(a, (\textbf{R}_{p(t)'}\textbf{R}_{p(t)})^n\textbf{R}_{p(t)'}\mathcal{P}_1(\{\textbf{F}_{p(t)}, \textbf{K}_{p(t)}\})), L)
    %% \lambda_{1}(t, T, a, L) := \cup_{n=0}^\infty\alpha_1^{(n)}(t, T, a, L)\\
    %% \lambda_{2}(t, T, a) := \cup_{n=0}^\infty\\
    \end{aligned}
  \right\}
\end{equation}
